HBots

### 2020-12-23 HBtos/article/tikzpictures/figure12.tex
cambios en los .tex para mejorar las figuras y cargarlas al repositorio remoto

\begin{document}

    \tikzstyle{miEstilo}= [thin, dotted, ]

        \begin{tikzpicture}

@@

            \path   (7.5,8)  node (a) [circle,draw] {0}
                    (3.5,4.5) node (b) [circle,draw] {0}
                    (11.5,4.5) node (c) [circle,draw] {0}
                    (1.5,2.5) node (d) [circle,draw] {0}
                    (5.5,2.5) node (e) [circle,draw] {0}
                    (9 .5,2.5) node (f) [circle,draw] {0}
                    (13.5,2.5) node (g) [circle,draw] {0}
                    (0.5,1) node (h) [circle,draw] {0}
                    (2.5,1) node (i) [circle,draw] {0}
                    (4.5,1) node (j) [circle,draw] {0}
                    (6.5,1) node (k) [circle,draw] {0}
                    (8.5,1) node (l) [circle,draw] {0}
                    (10.5,1) node (m) [circle,draw] {0}
                    (12.5,1) node (n) [circle,draw] {0}
                    (14.5,1) node (o) [circle,draw] {0}
                    (0,0) node (p) [circle,draw] {0}
                    (1,0) node (q) [circle,draw] {0}
                    (2,0) node (r) [circle,draw] {0}
                    (3,0) node (s) [circle,draw] {0}
                    (4,0) node (t) [circle,draw] {0}
                    (5,0) node (u) [circle,draw] {0}
                    (6,0) node (v) [circle,draw] {0}
                    (7,0) node (w) [circle,draw] {0}
                    (8,0) node (x) [circle,draw] {0}
                    (9,0) node (y) [circle,draw] {0}
                    (10,0) node (z) [circle,draw] {0}
                    (11,0) node (w5) [circle,draw] {0}
                    (12,0) node (w6) [circle,draw] {0}
                    (13,0) node (w7) [circle,draw] {0}
                    (14,0) node (w8) [circle,draw] {0}
                    (15,0) node (w9) [circle,draw] {0};

            \draw [fill=gray] (7.5,8) circle [radius=0.3];
            \draw [fill=gray] (3.5,4.5) circle [radius=0.3];
            \draw [fill=gray] (11.5,4.5) circle [radius=0.3];
            \draw [fill=gray] (1.5,2.5) circle [radius=0.3];
            \draw [fill=gray] (5.5,2.5) circle [radius=0.3];
            \draw [fill=gray] (9 .5,2.5) circle [radius=0.3];
            \draw [fill=gray] (13.5,2.5) circle [radius=0.3];
            \draw [fill=black] (0.5,1) circle [radius=0.3];
            \draw [fill=gray] (2.5,1) circle [radius=0.3];
            \draw [fill=gray] (4.5,1) circle [radius=0.3];
            \draw [fill=gray] (6.5,1) circle [radius=0.3];
            \draw [fill=gray] (8.5,1) circle [radius=0.3];
            \draw [fill=gray] (10.5,1) circle [radius=0.3];
            \draw [fill=gray] (12.5,1) circle [radius=0.3];
            \draw [fill=black] (14.5,1) circle [radius=0.3];
            \draw [fill=black] (0,0) circle [radius=0.3];
            \draw [fill=black] (1,0) circle [radius=0.3];
            \draw [fill=black] (2,0) circle [radius=0.3];
            \draw [fill=gray] (3,0) circle [radius=0.3];
            \draw [fill=black] (4,0) circle [radius=0.3];
            \draw [fill=gray] (5,0) circle [radius=0.3];
            \draw [fill=gray] (6,0) circle [radius=0.3];
            \draw [fill=black] (7,0) circle [radius=0.3];
            \draw [fill=black] (8,0) circle [radius=0.3];
            \draw [fill=gray] (9,0) circle [radius=0.3];
            \draw [fill=gray] (10,0) circle [radius=0.3];
            \draw [fill=black] (11,0) circle [radius=0.3];
            \draw [fill=gray] (12,0) circle [radius=0.3];
            \draw [fill=black] (13,0) circle [radius=0.3];
            \draw [fill=black] (14,0) circle [radius=0.3];
            \draw [fill=black] (15,0) circle [radius=0.3];

@@

            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =a ) -- (15.8,8);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =c ) -- (15.8,4.5);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =g ) -- (15.8,2.5);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =o ) -- (15.8,1);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =w9 ) -- (15.8,0);

>>>>

\begin{document}
        \begin{tikzpicture}[ultra thick]

@@

            \path   (7.5,6)  node (a) [circle,draw] {0}
                    (3.5,4.5) node (b) [circle,draw] {0}
                    (11.5,4.5) node (c) [circle,draw] {0}
                    (1.5,2.5) node (d) [circle,draw] {0}
                    (5.5,2.5) node (e) [circle,draw] {0}
                    (9 .5,2.5) node (f) [circle,draw] {0}
                    (13.5,2.5) node (g) [circle,draw] {0}
                    (0.5,1) node (h) [circle,draw] {0}
                    (2.5,1) node (i) [circle,draw] {0}
                    (4.5,1) node (j) [circle,draw] {0}
                    (6.5,1) node (k) [circle,draw] {0}
                    (8.5,1) node (l) [circle,draw] {0}
                    (10.5,1) node (m) [circle,draw] {0}
                    (12.5,1) node (n) [circle,draw] {0}
                    (14.5,1) node (o) [circle,draw] {0}
                    (0,0) node (p) [circle,draw] {0}
                    (1,0) node (q) [circle,draw] {0}
                    (2,0) node (r) [circle,draw] {0}
                    (3,0) node (s) [circle,draw] {0}
                    (4,0) node (t) [circle,draw] {0}
                    (5,0) node (u) [circle,draw] {0}
                    (6,0) node (v) [circle,draw] {0}
                    (7,0) node (w) [circle,draw] {0}
                    (8,0) node (x) [circle,draw] {0}
                    (9,0) node (y) [circle,draw] {0}
                    (10,0) node (z) [circle,draw] {0}
                    (11,0) node (w5) [circle,draw] {0}
                    (12,0) node (w6) [circle,draw] {0}
                    (13,0) node (w7) [circle,draw] {0}
                    (14,0) node (w8) [circle,draw] {0}
                    (15,0) node (w9) [circle,draw] {0};

            \draw [fill=gray] (7.5,6) circle [radius=0.3];
            \draw [fill=gray] (3.5,4.5) circle [radius=0.3];
            \draw [fill=gray] (11.5,4.5) circle [radius=0.3];
            \draw [fill=gray] (1.5,2.5) circle [radius=0.3];
            \draw [fill=gray] (5.5,2.5) circle [radius=0.3];
            \draw [fill=gray] (9 .5,2.5) circle [radius=0.3];
            \draw [fill=gray] (13.5,2.5) circle [radius=0.3];
            \draw [fill=black] (0.5,1) circle [radius=0.3];
            \draw [fill=gray] (2.5,1) circle [radius=0.3];
            \draw [fill=gray] (4.5,1) circle [radius=0.3];
            \draw [fill=gray] (6.5,1) circle [radius=0.3];
            \draw [fill=gray] (8.5,1) circle [radius=0.3];
            \draw [fill=gray] (10.5,1) circle [radius=0.3];
            \draw [fill=gray] (12.5,1) circle [radius=0.3];
            \draw [fill=black] (14.5,1) circle [radius=0.3];
            \draw [fill=black] (0,0) circle [radius=0.3];
            \draw [fill=black] (1,0) circle [radius=0.3];
            \draw [fill=black] (2,0) circle [radius=0.3];
            \draw [fill=gray] (3,0) circle [radius=0.3];
            \draw [fill=black] (4,0) circle [radius=0.3];
            \draw [fill=gray] (5,0) circle [radius=0.3];
            \draw [fill=gray] (6,0) circle [radius=0.3];
            \draw [fill=black] (7,0) circle [radius=0.3];
            \draw [fill=black] (8,0) circle [radius=0.3];
            \draw [fill=gray] (9,0) circle [radius=0.3];
            \draw [fill=gray] (10,0) circle [radius=0.3];
            \draw [fill=black] (11,0) circle [radius=0.3];
            \draw [fill=gray] (12,0) circle [radius=0.3];
            \draw [fill=black] (13,0) circle [radius=0.3];
            \draw [fill=black] (14,0) circle [radius=0.3];
            \draw [fill=black] (15,0) circle [radius=0.3];

@@

            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =a ) -- (15.8,6);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =c ) -- (15.8,4.5);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =g ) -- (15.8,2.5);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =o ) -- (15.8,1);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =w9 ) -- (15.8,0);

### 2020-12-23 HBtos/article/tikzpictures/figure7.tex

        \path   (8,10)  node (a) [circle,draw] {A}
                (5,9) node (b) [circle,draw] {B}
                (11,9) node (c) [circle,draw] {C}
                (4,8) node (d) [circle,draw] {D}
                (6,8) node (e) [circle,draw] {E}
                (10,8) node (f) [circle,draw] {F}
                (12,8) node (g) [circle,draw] {G}
                (3,7) node (h) [circle,draw] {H}
                (5,7) node (i) [circle,draw] {I}
                (7,7) node (j) [circle,draw] {J}
                (9,7) node (k) [circle,draw] {K}
                (11,7) node (l) [circle,draw] {L}
                (13,7) node (m) [circle,draw] {M}
                (3,5) node (n) [circle,draw] {N}
                (5,5) node (o) [circle,draw] {O}
                (7,5) node (p) [circle,draw] {P}
                (9,5) node (q) [circle,draw] {Q}
                (11,5) node (r) [circle,draw] {R}
                (13,5) node (s) [circle,draw] {S};

>>>>

        \path   (8,10)  node (a) [circle,draw] {A}
                (5,9) node (b) [circle,draw] {B}
                (11,9) node (c) [circle,draw] {C}
                (4,8) node (d) [circle,draw] {D}
                (6,8) node (e) [circle,draw] {E}
                (10,8) node (f) [circle,draw] {F}
                (12,8) node (g) [circle,draw] {G}
                (3,7) node (h) [circle,draw] {H}
                (5,7) node (i) [circle,draw] {I}
                (7,7) node (j) [circle,draw] {J}
                (9,7) node (k) [circle,draw] {K}
                (11,7) node (l) [circle,draw] {L}
                (13,7) node (m) [circle,draw] {M}
                (3,5.5) node (n) [circle,draw] {N}
                (5,5.5) node (o) [circle,draw] {O}
                (7,5.5) node (p) [circle,draw] {P}
                (9,5.5) node (q) [circle,draw] {Q}
                (11,5.5) node (r) [circle,draw] {R}
                (13,5.5) node (s) [circle,draw] {S};
